DraftOne

### 2016-06-10 DraftOne.Rmd
Fixing sim_data function

        require(dplyr)
        t <- calc_t(n, trend)
        if(x_type == "binary" & trend = "constant"){
                x <- binary_exposure(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend=="constant"){
                x <- continuous_exposure(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        } else if(x_type == "binary" & trend != "constant"){
                x <- season_binexp(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend != "constant"){
                x <- season_contexp(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        }

        if(trend == "constant"){
                exp_base_y <- constant_baseline(n = n, ...)
        }

        df <- full_join(x, exp_base_y, by = "date") %>%
                mutate(exp_y = exp(log(exp_base_y) + log(rr) * x))
        df$y <- sapply(df$exp_y, FUN = function(x) rpois(1, x))

        return(df)

>>>>

        require(dplyr)

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, ...)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
        else if(trend != "constant"){
          if(x_type == "binary"){
            x <- season_binexp(n = n,...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, ...)
          }

        }
  return(df)
}

#????

        if(x_type == "binary" & trend == "constant"){
                x <- binary_exposure(n = n, ...)
                exp_base_y <- constant_baseline(n=n, ...)
                df <- full_join(x, exp_base_y, by="date")
                df <- mutate(df, exp_y=exp(log(exp_base_y)+log(rr)*x))
                df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        } else if(x_type == "continuous" & trend=="constant"){
                x <- continuous_exposure(n = n, ...)
                exp_base_y <- constant_baseline(n=n, ...)
                df <- full_join(x, exp_base_y, by="date")
                df <- mutate(df, exp_y=exp(log(exp_base_y)+log(rr)*x))
                df$y <- sapply(df$exp_y, FUN=function(x) rpois(1,x))

        } else if(x_type == "binary" & trend != "constant"){
                x <- season_binexp(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend != "constant"){
                x <- season_contexp(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        }
        return(df)
